# .R and helpfiles

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

- `.R` files contain the functions your packge will provide
- Don't code helpfiles (`.Rd` files in the `man` folder) yourself 
- Use Roxygen syntax through the [roxygen2 package](https://github.com/r-lib/roxygen2)
  - Roxygen syntax lines begin `#' `
- To additionally use markdown syntax within roxygen syntax add the following line to your `DESCRIPTION` file
```
Roxygen: list(markdown = TRUE)
```
- Your `.R` files will look something like the following, i.e., roxygen code for the helpfile for a function before the actual R code of the function
```{r, eval=FALSE, echo=TRUE}
#' The length of a string
#'
#' Technically this returns the number of "code points", in a string. One
#' code point usually corresponds to one character, but not always. For example,
#' an u with a umlaut might be represented as a single character or as the
#' combination a u and an umlaut.
#'
#' @inheritParams str_detect
#' @return A numeric vector giving number of characters (code points) in each
#'    element of the character vector. Missing string have missing length.
#' @seealso [stringi::stri_length()] which this function wraps.
#' @export
#' @examples
#' str_length(letters)
#' str_length(NA)
#' str_length(factor("abc"))
#' str_length(c("i", "like", "programming", NA))
str_length <- function(string) {
  ...
}
```
- Running `devtools::document()` will generate your `.Rd` files from your `.R` files
